Reducing Acceptance Marks in Emerson-Lei Automata by QBF Solving

### 2023-06-03 paper/main.tex
minor changes

\begin{table}[t]
  \caption{Considered translators and the numbers of \emph{fails} and
    successfully constructed automata with \emph{at most 1 mark} and
    with \emph{at least 2 marks} for each translator and set of
    formulas.}
\label{tab:ltltranslators}
\centering
% \begin{tabular}{lr@{~~~~~~}lr}
% \toprule
% tool        & version&homepage & ~~~automata \\
% \midrule
% \texttt{ltl2dela}~~~ & 21.0 & \multirow{2}{*}{\url{https://owl.model.in.tum.de/}} & 129\\
% \texttt{ltl2dgra} & 21.0 & & 234\\
% \texttt{ltl2tgba} & 2.10.4 & \url{https://spot.lrde.epita.fr} & 70\\
% \texttt{ltl3tela} & 2.2.0  & \url{https://github.com/jurajmajor/ltl3tela} & 91\\
% \bottomrule
% \end{tabular}
%
% \begin{tabular}{lrrrr}
%   \toprule
%   &&& \multicolumn{2}{c}{constructed automata with} \\ \cmidrule(lr){4-5}
%   tool &\!\!\!version/homepage & ~~~~fails & less than 2 marks & \textbf{at least 2 marks}\\
%   \midrule
%   \texttt{ltl2dela} & 21.0\tablefootnote{\label{fn:owl}\url{https://owl.model.in.tum.de/}}
%        & 5 & 214 & \textbf{129} \\
%   \texttt{ltl2dgra} & 21.0\footnotemark[1]
%        & 12 & 102 & \textbf{234}\\
%   \texttt{ltl2tgba} & 2.10.4\tablefootnote{\url{https://spot.lrde.epita.fr}}
%        & 0 & 278 & \textbf{70}\\
%   \texttt{ltl3tela} & 2.2.0\tablefootnote{\url{https://github.com/jurajmajor/ltl3tela}}
%        & 18 & 239 & \textbf{91}\\
%   \bottomrule
% \end{tabular}
%
\setlength{\tabcolsep}{5.7pt}
\begin{tabular}{lrrrrrrr}
  \toprule
  && \multicolumn{3}{c}{\!348 formulas from literature\!} & \multicolumn{3}{c}{366 random formulas}\\
  \cmidrule(lr){3-5} \cmidrule(lr){6-8}
  &&& \multicolumn{2}{c}{automata with} && \multicolumn{2}{c}{automata with}\\
  \cmidrule(lr){4-5} \cmidrule(lr){7-8}
  \multicolumn{2}{l}{translator ~~~ (version)$^{\text{web}}$}
  & ~~~~fails & \makecell[r]{at most\\[-1ex] 1 mark} & \makecell[r]{\textbf{at least}\\[-1ex] \textbf{2 marks}}
  & ~~~~fails & \makecell[r]{at most\\[-1ex] 1 mark} & \makecell[r]{\textbf{at least}\\[-1ex] \textbf{2 marks}}\\
  % &&& at most & \textbf{at least} && at most & \textbf{at least}\\[-.8ex]
  % \multicolumn{2}{l}{translator ~~~ (version)$^{\text{web}}$} & ~~~~fails & 1 mark & \!\!\!\!\textbf{2 marks} & ~~~~fails & 1 mark & \!\!\!\!\textbf{2 marks}\\
  \midrule 
  \texttt{ltl2tgba -G} & (2.10.4)\tablefootnote{\url{https://spot.lrde.epita.fr}}
  & 0 & 278 & \textbf{70} & ? & ? & \textbf{?}\\
  \texttt{ltl3tela} & (2.2.0)\tablefootnote{\url{https://github.com/jurajmajor/ltl3tela}}
  & 18 & 239 & \textbf{91} & ? & ? & \textbf{?}\\
  \texttt{ltl3tela -D1} & (2.2.0)\footnotemark[2]
  & ? & ? & \textbf{?} & ? & ? & \textbf{?}\\ 
  \texttt{ltl2dela} & (21.0)\tablefootnote{\label{fn:owl}\url{https://owl.model.in.tum.de/}}
  & 5 & 214 & \textbf{129} & ? & ? & \textbf{?}\\
  \texttt{ltl2dgra} & (21.0)\footnotemark[3]
  & 12 & 102 & \textbf{234} & ? & ? & \textbf{?}\\
  \bottomrule
\end{tabular}
\end{table}

>>>>

\begin{table}[t]
  \caption{Considered translators and the numbers of \emph{fails} and
    successfully constructed automata with \emph{at most 1 mark} and
    with \emph{at least 2 marks} for each translator and set of
    formulas.}
\label{tab:ltltranslators}
\centering
% \begin{tabular}{lr@{~~~~~~}lr}
% \toprule
% tool        & version&homepage & ~~~automata \\
% \midrule
% \texttt{ltl2dela}~~~ & 21.0 & \multirow{2}{*}{\url{https://owl.model.in.tum.de/}} & 129\\
% \texttt{ltl2dgra} & 21.0 & & 234\\
% \texttt{ltl2tgba} & 2.10.4 & \url{https://spot.lrde.epita.fr} & 70\\
% \texttt{ltl3tela} & 2.2.0  & \url{https://github.com/jurajmajor/ltl3tela} & 91\\
% \bottomrule
% \end{tabular}
%
% \begin{tabular}{lrrrr}
%   \toprule
%   &&& \multicolumn{2}{c}{constructed automata with} \\ \cmidrule(lr){4-5}
%   tool &\!\!\!version/homepage & ~~~~fails & less than 2 marks & \textbf{at least 2 marks}\\
%   \midrule
%   \texttt{ltl2dela} & 21.0\tablefootnote{\label{fn:owl}\url{https://owl.model.in.tum.de/}}
%        & 5 & 214 & \textbf{129} \\
%   \texttt{ltl2dgra} & 21.0\footnotemark[1]
%        & 12 & 102 & \textbf{234}\\
%   \texttt{ltl2tgba} & 2.10.4\tablefootnote{\url{https://spot.lrde.epita.fr}}
%        & 0 & 278 & \textbf{70}\\
%   \texttt{ltl3tela} & 2.2.0\tablefootnote{\url{https://github.com/jurajmajor/ltl3tela}}
%        & 18 & 239 & \textbf{91}\\
%   \bottomrule
% \end{tabular}
%
\setlength{\tabcolsep}{5.7pt}
\begin{tabular}{lrrrrrrr}
  \toprule
  && \multicolumn{3}{c}{\!348 formulas from literature\!} & \multicolumn{3}{c}{335 random formulas}\\
  \cmidrule(lr){3-5} \cmidrule(lr){6-8}
  &&& \multicolumn{2}{c}{automata with} && \multicolumn{2}{c}{automata with}\\
  \cmidrule(lr){4-5} \cmidrule(lr){7-8}
  \multicolumn{2}{l}{translator ~~~ (version)$^{\text{web}}$}
  & ~~~~fails & \makecell[r]{at most\\[-1ex] 1 mark} & \makecell[r]{\textbf{at least}\\[-1ex] \textbf{2 marks}}
  & ~~~~fails & \makecell[r]{at most\\[-1ex] 1 mark} & \makecell[r]{\textbf{at least}\\[-1ex] \textbf{2 marks}}\\
  % &&& at most & \textbf{at least} && at most & \textbf{at least}\\[-.8ex]
  % \multicolumn{2}{l}{translator ~~~ (version)$^{\text{web}}$} & ~~~~fails & 1 mark & \!\!\!\!\textbf{2 marks} & ~~~~fails & 1 mark & \!\!\!\!\textbf{2 marks}\\
  \midrule 
  \texttt{ltl2tgba -G} & (2.10.4)\tablefootnote{\url{https://spot.lrde.epita.fr}}
  & 0 & 278 & \textbf{70} & 0 & 320 & \textbf{15}\\
  \texttt{ltl3tela} & (2.2.0)\tablefootnote{\url{https://github.com/jurajmajor/ltl3tela}}
  & 18 & 239 & \textbf{91} & 0 & 286 & \textbf{49}\\
  \texttt{ltl3tela -D1} & (2.2.0)\footnotemark[2]
  & 20 & 247 & \textbf{81} & 0 & 291 & \textbf{44}\\ 
  \texttt{ltl2dela} & (21.0)\tablefootnote{\label{fn:owl}\url{https://owl.model.in.tum.de/}}
  & 5 & 214 & \textbf{129} & 0 & 246 & \textbf{89}\\
  \texttt{ltl2dgra} & (21.0)\footnotemark[3]
  & 12 & 102 & \textbf{234} & 0 & 130 & \textbf{205}\\
  \bottomrule
\end{tabular}
\end{table}
